\Author{\daAuthorTwo}

\section{Management of the project}

In this section, the managing process and structure will be described.

\subsection{Overview}
We managed our project using the scrum methodology. After all requirements were defined, we came together as a team and decided on a rough timeline for our project. We defined the following milestones:

\begin{description}
    \item [30.06.2024:] designed database relations
    \item [30.07.2024:] designed UI of mobile app 
    \item [30.07.2024:] designed UI of admin panel
    \item [30.10.2024:] implemented backend
    \item [30.10.2024:] implemented mobile app
    \item [30.11.2024:] implemented admin panel
    \item [15.12.2024:] first tests through end users
\end{description}

Following this plan, we had enough time to implement all features and were able to still make changes in the final days before deployment. 

\subsection{User stories}

We also defined multiple different user stories that we implemented over the course of multiple sprints, some of them we will list in the following.

\begin{itemize}
    \item As a user, I want to see an input address that I need to visit highlighted on a map based on OpenStreetMap.
    \item As a user, I want to be able to select an address and write a comment for it.
    \item As a user, I want to be able to check addresses that I visited.
    \item As a user, I want to be able to differentiate special addresses from normal ones I need to visit on the map. (Homes that should be left out, Place to eat for the day)
\end{itemize}

We made use of a "Scrum-Lite", which was more suitable for this project, as we often discussed the current progress in breaks between lessons, rather than having a dedicated meeting every day. Not strictly following all scrum guidelines enabled us to benefit from scrums' advantages without adding organizational overhead. We also had regular meetings with our supervisor to also keep him up-to-date with on the progress we made. This was also beneficial to us because of the slight pressure it provided.

\newpage