\Author{\daAuthorTwo}

In this section, the process of how the app got introduced to the users and their feedback will be examined.

\subsection{Introducing new users}

Exactly as agreed upon, in the year 2025 only four groups actually used our app during the campaign. We had a personal meeting with the supervisors of the mentioned groups. All of them could be categorized as individuals with an average understanding of technology. We demonstrated the functionality of the app briefly and explained what our goals were. Also, the administrator was at this meeting, so we quickly showed her around the Admin Panel. This was a very short rundown of the functionality, but nevertheless, she figured it all out. After this short meeting, we helped them with the installation and sent them on their way. During the campaign, we sometimes took a look into our Admin Panel and could see that each user reliably checked off her visited houses.  

\subsection{User Feedback}

After the campaign, we once again came together for a short recap on the experience of using the app. There were a few key points that every one of the testers mentioned. First of all, the inclusion of more states for if an address was visited. This was the main talking point and will definitely be improved in a future version. Secondly. the inclusion of a live location was wished for, as well as the perception of long loading times. Overall, the feedback was very positive, and therefore the project will definitely be continued after the finalization of this thesis. 

\newpage