%! Author = weiss
%! Date = 20.01.2025
\Author{\daAuthorThree}

    \section{Area Borders}
    The area borders feature addresses the research question by implementing computational geometry algorithms for precise geographical boundary calculations.

    \subsection{Purpose of Area Borders in the App}
    Accurate area borders are essential for defining regions based on user input, supporting the app's mapping functionality.

    \subsection{Overview of the Convex Hull Algorithm}
    The convex hull algorithm identifies the smallest convex polygon enclosing a set of points, making it a suitable choice for this project.

    \subsection{Use Cases of the Convex Hull in Industry}
    Applications of convex hulls in mapping, computer graphics, and robotics highlight their importance in solving real-world problems.

    \subsection{Alternate Methods for Area Border Calculation}
    Alternative methods like Voronoi diagrams and alpha shapes were considered but found less suitable due to complexity or computational demands.

    \subsection{Rationale for Choosing the Convex Hull Method}
    The convex hull algorithm offers a balance of simplicity, efficiency, and accuracy, aligning with the project's requirements.

    \subsection{Integration of the Algorithm into the Backend}
    The algorithm is implemented in the service layer, ensuring smooth integration with other backend components.

    \subsection{Challenges and Adjustments}
    Challenges included handling edge cases like collinear points, which were resolved through specific algorithm adjustments.
